---
title: "Chapter13"
author: "Xinqian Cai"
date: "2022/2/21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## 1. Load the `dengue.csv` file provided to you

```{r}
file <- "C:/Users/Tracy/Desktop/DUKE/第三学期/SOC723/SOC723/dengue.csv"

dengue <- read.csv(file)

```

## 2. Run an OLS regression using average humidity to predict whether dengue was observed in the area, and look at the results.

```{r}
library(tidyverse)
library(broom)
library(modelsummary)
library(margins)
# This is the direct OLS regression
m2<-lm(NoYes~humid,data=dengue)
msummary(models = list(m2), stars=c('*' = .1, '**' = .05, '***' = .01))
summary(m2,stars=TRUE)

# Since the dependent variable is binomial variable, so I also put logiistic regression here.
m2l<-glm(NoYes~humid,data=dengue, family = binomial)
msummary(models = list(m2l), stars=c('*' = .1, '**' = .05, '***' = .01))
summary(m2l,stars=TRUE)

```

## 3. Write two sentences, one interpreting the intercept and one interpreting the slope.

```{r}

## For the OLS regression
# For the intercept, it means that when the average humidity is 0, the probability of observing dengue in the area is -6.31570.

# For the slope, it means that a one-unit increase in humidity is associated with a 0.049758-unit change in the probability of observing dengune in the area.


## For the logit regression

# For the intercept, it means that when the average humidity is 0,the probability of observing dengue in the area is about 0.0018.
prob0<-exp(-6.31570 )/(1+exp(-6.31570 ))
prob0

# For the slope, it means that a one-unit increase in humidity is associated with a (0.33605*Pr(Y=1)*(1-Pr(Y=1))-unit change in the possibility that dengue is observed in the area.
```

## 4. Get a set of summary statistics for the humidity variable and write a comment on how this can help you make sense of the intercept in the regression from step 2.

```{r}
summary(dengue$humid)

# From the summary statistics for the humidity variable, we can see that the minimum value of the average humidity is 0.6714, which means that it is impossible to have 0 humidity. So the intercept (when humidity is 0) is just a statistical number in the regression, it does not have much realistic meaning. (In reality, it is impossible that the possibility will be less than 0.)
```


## 5. We might recognize that, if we're interested in the effect of humidity on Dengue, temperature might be on a back door. Add a control for temperature, rerun the regression, and show the results.

```{r}
# For the OLS
m5<-lm(NoYes~humid+temp,data=dengue)
msummary(models = list(m5), stars=c('*' = .1, '**' = .05, '***' = .01))
summary(m5,stars=TRUE)

# For the logit regression
m5l<-glm(NoYes~humid+temp,data=dengue,family=binomial(link = 'logit'))
msummary(models = list(m5l), stars=c('*' = .1, '**' = .05, '***' = .01))
summary(m5l,stars=TRUE)
```

## 6.Our dependent variable is binary, and we're getting predictions below zero, which we might not want. Rerun the regression from question 5 but as a logit model, and report the marginal effects of both slope coefficients.

```{r}
m6<-glm(NoYes~humid+temp,data=dengue,family=binomial(link = 'logit'))
msummary(models = list(m6), stars=c('*' = .1, '**' = .05, '***' = .01))
summary(m6,stars=TRUE)

#The marginal effects of humidity is that when controlling for temperature, a one-unit increase in humidity is associated with a (0.30474*Pr(Y=1)*(1-Pr(Y=1))-unit change in the possibility of observing dengue in the area.

#The marginal effects of temperature is that when controlling for humidity, a one-unit increase in temperature is associated with a (0.03987*Pr(Y=1)*(1-Pr(Y=1))-unit change in the possibility of observing dengue in the area.
```


## 7.  A long one: Now let's say we're directly interested in the relationship between temperature and humidity. Run an OLS regression of humidity on temperature. Calculate the residuals of that regression, and then make a plot that will let you evaluate whether there is likely heteroskedasticity in the model. Rerun the model with heteroskedasticity-robust standard errors. Show both models, and say whether you think there is heteroskedasticity

*Language-specific instructions*: 

- In both R and Python, save the model as `m7`, and `m7b` if you rerun with robust standard errors. 

In R, use `fiter(!is.na(dengue$humid))` on the data before running the model so the residuals line up properly. Use the `msummary()` function from the **modelsummary** package to display the results with the `stars = TRUE` option. Also, if you're clever about `msummary()` usage, you can skip creating `m7b`. You can access residuals using `resid(m7)`.

```{r}
dengue7<-dengue|>
  filter(!is.na(dengue$humid))
#load packages
library(tidyverse)
library(AER)
library(sandwich)
library(fixest)

# Regression
m7<-lm(humid~temp,data = dengue7)
msummary(models = list(m7), stars=c('*' = .1, '**' = .05, '***' = .01))

#Residual
res<-resid(m7)

#Plot residuals
plot(fitted(m7), res, xlab = "temp", main = "heteroskedasticity check")
# Based on the plot, I think there is likely heteroskedasticity in the model. For the low temperature around -10, the residuals is high referring to greater error than the other temperature intervals.For the temperature from 0-10, the residuals seem to close to each other, but lower than that of the temperature around -10. For the temperature from 10-20, the residuals seem to vary more than the temperature from 0-10, and most of these residuals seems greater than those in temperature from 0-10. So I think there is likely heteroskedasticity in the model.

# Rerun model
m7b<-feols(humid~temp,data = dengue7, se='hetero')
msummary(models = list(m7,m7b), stars=c('*' = .1, '**' = .05, '***' = .01))

# I do think that there is heteroskedasticity because the standard error for the coeffcient of temperature in model 1 without heteroskedasticity-adujustment is smaller than in model 2 with heteroskedasticity-adujustment


```


## 8. In the graph in the last problem you may have noticed that for certain ranges of temperate, the errors were clearly nonzero on average. This can indicate a functional form problem. Run the model from question 7 again (with heteroskedasticity-robust standard errors), but this time use the logarithm of humidity in place of humidity. Add a sentence interpreting the coefficient on temperature. 


```{r}
m8<-feols(log(humid)~temp,data = dengue7, se='hetero')
msummary(models = m8, stars=c('*' = .1, '**' = .05, '***' = .01))

# A one-unit change in temperature is associated with a 0.056-unit change in In(humid), which means a 5.6-unit change in humidity.

```

## 9. Bonus challenge: figure out how I decided on a form where you log humidity and keep temperature linear.

```{r}

modela<-lm(log(humid)~temp, data = dengue)
modelb<-lm(humid~log(temp), data = dengue)
modelc<-lm(log(humid)~log(temp), data = dengue)

msummary(models = list(modela,modelb,modelc), stars = TRUE)

# From the statistics below, we can see that both AIC and BIC of modela with logging humidity and keeping temperature linear is the smallest among the three models. Therefore, it seems that model a with logging humidity and keeping temperature linear performs best.
```





